### 2022-12-11 doc/manuscript/translocation.qmd
Address comments in manuscript, add table, update figure

![A. The predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and probability of recruitment $\omega$, given the parameterized, deterministic model for translocated *R. sierrae*. Colored points show the predicted $\lambda$ values for the twelve translocated populations when probability of recruitment into the adult class is $\omega = 0.1$ (given by the dashed line). B. The predicted fifty-year extinction probabilities of the twelve translocated populations given demographic stochasticity, environmental variability in $\omega$, and different mean values of $\omega$. The dashed line shows where $\omega = 0.1$, for comparison to A.](figures/pop_viability_figures_for_manuscript_v1.jpg){#fig-viability}

<!-- Use figure v1 or v2 (omega = 0.3)? If v1, sort legend labels by sigma-AR-->

![A. The elasticity of $\lambda$ with changes in three parameters: $\sigma_{A_R}$, $\omega$, and *F (*number of eggs produced by a female frog in a year that successfully hatch). Elasticity is calculated at the default parameter values for each population and $\omega$ = 0.1. B. The 100 simulated trajectories (black lines) that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (colored line).](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp}

<!-- In legend for (A), change "lake" to "site". Switch color of 70550 in A so that color of associated line in B can be easily referenced in text, e.g., "orange". Also, use colorblind-friendly palette for figure, if possible. -->

@@

The parameters in this model are yearly survival probability $\sigma_{*}$, where the "\*" indicates a particular state variable<!--# "*" subscript is not translating correctly in .docx. Shows as upsidedown question mark -->, the probability that a female frog reproduces in a given year $p_F$, the number of eggs produced by a female frog in a year that successfully hatch $F$, the probability of a first year tadpole remaining as a tadpole $p_{L1}$, the probability of a second year tadpole remaining as a tadpole $p_{L2}$, and the probability of a first year juvenile remaining as a juvenile $p_{J1}$. The parameter $\omega$ gives the probability of a juvenile successfully recruiting to an adult.

@@

The baseline parameter values for the model and how they were estimated are given in Table 1 <!--# Create table --> . Parameters $\sigma_{A_T}$ and $\sigma_{A_R}$ were extracted directly from our CMR model described elsewhere. For populations where we had a sufficient number of pit-tagged, naturally recruited adults, we observed that $\sigma_{A_T}$ and $\sigma_{A_R}$ could be notably different, with $\sigma_{A_R} > \sigma_{A_T}$. For populations lacking any naturally-recruited adults, we were unable to directly estimate $\sigma_{A_R}$, and instead set $\sigma_{A_R} = \sigma_{A_T}$.

@@

We performed four analyses on our model. First, we considered a deterministic version of our model with no yearly heterogeneity in probability of successful recruitment $\omega$, and calculated the predicted long-run growth rate $\lambda$ of a population for different values of $\sigma_{A_R}$ and $\omega$. We then fixed $\omega = 0.1$ and calculated the predicted growth rate of our six populations.

Second, we performed a local sensitivity analysis <!--# referred to elsewhere as "elasticity" -->on $\lambda$ with respect to parameters $\omega$, $\sigma_{A_R}$, and $F$ to determine how small changes in these parameters could influence the long-run deterministic growth rate of populations.

Third, we defined a version of the model with demographic and environmental stochasticity, where environmental stochasticity was represented by among-year variability in $\omega$. We used this model to simulate a one-time introduction of 40 translocated adult frogs. We ran this simulation 1000 times for each population and computed the probability of a population becoming extinct after 50 years given the observed parameter values and environmental stochasticity in $\omega$. We varied the mean recruitment probability $\omega$ from 0.05 and 0.3 and drew values of $\omega$ each year from a beta distribution with a dispersion parameter of $\phi = 2$ (when $\omega = 0.5$ and $\phi = 2$ the beta distribution is uniform between 0 and 1).

>>>>

![A. The predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and probability of recruitment $\omega$, given the parameterized, deterministic model for translocated *R. sierrae*. Colored points show the predicted $\lambda$ values for the twelve translocated populations when probability of recruitment into the adult class is $\omega = 0.3$ (given by the dashed line). B. The predicted fifty-year extinction probabilities of the twelve translocated populations given demographic stochasticity, environmental variability in $\omega$, and different mean values of $\omega$. The dashed line shows where $\omega = 0.3$, for comparison to A.](figures/pop_viability_figures_for_manuscript_v2.jpg){#fig-viability}

![A. The elasticity of $\lambda$ with changes in three parameters: $\sigma_{A_R}$, $\omega$, and *F (*number of eggs produced by a female frog in a year that successfully hatch). Elasticity is calculated at the default parameter values for each population and $\omega$ = 0.3. B. The 100 simulated trajectories (black lines) that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (light orange).](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp}

<!-- Left color palette as is as 12-color color-blind friendly is not the most friendly color palette to look at.  We can discuss. -->

@@

The parameters in this model are yearly survival probability $\sigma_{\cdot}$, where the "$\cdot$" indicates a particular state variable, the probability that a female frog reproduces in a given year $p_F$, the number of eggs produced by a female frog in a year that successfully hatch $F$, the probability of a first year tadpole remaining as a tadpole $p_{L1}$, the probability of a second year tadpole remaining as a tadpole $p_{L2}$, and the probability of a first year juvenile remaining as a juvenile $p_{J1}$. The parameter $\omega$ gives the probability of a juvenile successfully recruiting to an adult.

@@

The baseline parameter values for the model and how they were estimated are given in Table 1. Parameters $\sigma_{A_T}$ and $\sigma_{A_R}$ were extracted directly from our CMR model described previously in this study. For populations where we had a sufficient number of pit-tagged, naturally recruited adults, we observed that $\sigma_{A_T}$ and $\sigma_{A_R}$ could be notably different, with $\sigma_{A_R} > \sigma_{A_T}$. For populations lacking any naturally-recruited adults, we were unable to directly estimate $\sigma_{A_R}$, and instead set $\sigma_{A_R} = \sigma_{A_T}$.

Table 1: Description and values of parameters used in the model. All survival probabilities are in the presence of the fungal pathogen Bd. <!--# Roland, please add any additional details needed to the "Source" column.  We ideally want to keep this succinct.  -->

| **Parameter**                                                             | **Value**            | **Source**                                                             |
|:----------------------------|:------------------|:-----------------------|
| $\sigma_{L_1}$, Yearly survival probability of year 1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge     |
| $\sigma_{L_2}$, Yearly survival probability of year 2 tadpoles            | 0.7                  | Estimated from field data, observations, and natural history knowledge |
| $\sigma_{L_3}$, Yearly survival probability of year 3 tadpoles            | 0.7                  | Estimated from field data, observations, and natural history knowledge |
| $\sigma_{J_1}$, Yearly survival probability of year 1 juveniles           | 0.25                 | Estimated from field data, observations, natural history knowledge     |
| $\sigma_{J_2}$, Yearly survival probability of year 2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge     |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from mark-recapture studies                                  |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from mark-recapture studies                                  |
| $p_{L_1}$, Probability of a year 1 larvae remaining as a larvae           | 1                    | Estimated from field data, observations, and natural history knowledge |
| $p_{L_2}$, Probability of a year 2 larvae remaining as a larvae           | 0.25                 | Estimated from field data, observations, and natural history knowledge |
| $p_{J_1}$, Probability of a year 1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, and natural history knowledge |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                     |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                     |
| $\omega$, Probability of juvenile successfully recruiting to an adult     | Varies yearly        | Explored different values of this parameter                            |

@@

We performed four analyses on our model. First, we considered a deterministic version of our model with no yearly heterogeneity in probability of successful recruitment $\omega$, and calculated the predicted long-run growth rate $\lambda$ of a population for different values of $\sigma_{A_R}$ and $\omega$. We then fixed $\omega = 0.3$ and calculated the predicted growth rate of our 12 populations.

Second, we performed a local elasticity analysis on $\lambda$ with respect to parameters $\omega$, $\sigma_{A_R}$, and $F$ to determine how small changes in these parameters could influence the long-run deterministic growth rate of populations.

Third, we defined a version of the model with demographic and environmental stochasticity, where environmental stochasticity was represented by among-year variability in $\omega$. We used this model to simulate a one-time introduction of 40 translocated adult frogs. We ran this simulation 1000 times for each population and computed the probability of a population becoming extinct after 50 years given the observed parameter values and environmental stochasticity in $\omega$. We varied the mean recruitment probability $\omega$ from 0.15 and 0.4 and drew values of $\omega$ each year from a beta distribution with a dispersion parameter of $\phi = 2$ (when $\omega = 0.5$ and $\phi = 2$ the beta distribution is uniform between 0 and 1).
